Response to Reviewers' Comments

### 2025-02-05 review/review.tex
Fixed review ref and typos

This document provides responses to the reviewers' comments. First of all, we would like to sincerely thank the reviewers for their thoughtful and constructive feedback. We feel that their input has enhanced the clarity and quality of this manuscript a lot, and we appreciate their efforts to improve our article.

@@

	      \answer{Thanks for your remarks that has given us plenty to think about. We have answered to this remarks in a dedicated Section \ref{sec:evaluation_of_the_number_of_iterations_for_convergence} at the end of this document.}

@@

@@

\section{Sketch of Proof Mesh-Height Map Intersection}
\label{sec:sketch_of_proof_mesh_height_map_intersection}

>>>>

This document provides responses to the reviewers' comments. First, we would like to sincerely thank the reviewers for their thoughtful and constructive feedback. We feel that their input has enhanced the clarity and quality of this manuscript a lot, and we appreciate their efforts to improve our article.

@@

	      \answer{Thanks for your remarks that has given us plenty to think about. We have answered to this remarks in a dedicated Appendix \ref{sec:sketch_of_proof} at the end of this document.}

@@

	      \answer{As mention before, we have added more details about the implementation to clarify this part.}

@@

\section{Sketch of Proof Mesh-Height Map Intersection}
\label{sec:sketch_of_proof}
